---
title: "Global HIV/AIDS Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load the libraries
library("dplyr")
library("plotly")
library("ggplot2")
library("leaflet")
library("tidyverse")
library("knitr")

# Loading data
hiv_df <- read.csv("data/art_coverage_by_country_clean.csv",
  stringsAsFactors = FALSE
)

# Data for country coordinates
country_coordinates <- read.csv("data/world_country_coordinate.csv",
  stringsAsFactors = FALSE
)
```

## Introduction 
The data was collected and generated by WHO and UNESCO from their public records on the number of people living with HIV/AIDS around the world. Devakumar cleaned that data from WHO and UNESCO and put the data into a CSV file that draws a focus on treatment statistics for those living with HIV/AIDS by country.There are 170 observations (rows) in the HIV/AIDS dataset and 10 features (columns) in the HIV/AIDS dataset. With this dataset
we are going to try and view the extent of treatment coverage is for HIV/AIDS in countries globally, ART treatment's impact on the number of people living with HIV, and compare the amount of people living with HIV by region.

## Summary Information

```{r summary, echo=FALSE, warning=FALSE}
source("scripts/summaryinfo.R")
get_summary_info(hiv_df)
```

## Aggregate Table

```{r aggregate-table, echo=FALSE, warning=FALSE}
source("scripts/tablesummary.R")
kable(summary_table(hiv_df))
```

## Charts

```{r firstchart, echo=FALSE, warning=FALSE}
source("scripts/firstchart.R")
geographical_chart(hiv_df, country_coordinates)
```

```{r thirdchart, echo=FALSE, warning=FALSE}
source("scripts/thirdchart.R")
plot_hiv_per_region(hiv_df)
```
This chart was intended to show the relationship between the number of HIV cases and the region of the world. The chart's goal was to help us figure out what region has been impacted the most by the HIV crisis. It is clear from looking at the bar chart that the African region has been hit the hardest, with 25.5 million estimated cases. It has the highest total of estimated HIV cases than any other region. In fact, it has more cases than every other region put together. The next highest region is the America's with 2.3 million estimated cases. The Eastern Mediterranean region has the lowest amount of cases, with 380 thousand cases. Most of the world's focus in dealing with the HIV crisis should be centered on helping Africa. 

```{r secondchart.R, echo=FALSE}
source("scripts/secondchart.R")
Art_treated_vs_sick(hiv_df)
```
