---
title: "Global HIV/AIDS Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load the libraries
library("dplyr")
library("plotly")
library("ggplot2")
library("leaflet")

# Loading data
hiv_df <- read.csv("data/art_coverage_by_country_clean.csv",
  stringsAsFactors = FALSE
)

# Data for country coordinates
country_coordinates <- read.csv("data/world_country_coordinate.csv",
  stringsAsFactors = FALSE
)
```

## Introduction 
The data was collected and generated by WHO and UNESCO from their public records on the number of people living with HIV/AIDS around the world. Devakumar cleaned that data from WHO and UNESCO and put the data into a CSV file that draws a focus on treatment statistics for those living with HIV/AIDS by country.There are 170 observations (rows) in the HIV/AIDS dataset and 10 features (columns) in the HIV/AIDS dataset. With this dataset
we are going to try and view the extent of treatment coverage is for HIV/AIDS in countries globally, ART treatment's impact on the number of people living with HIV, and compare the amount of people living with HIV by region.

## Summary Information

## Aggregate Table

## Charts

```{r firstchart, echo=FALSE, warning=FALSE}
source("scripts/firstchart.R")
geographical_chart(hiv_df, country_coordinates)
```

```{r thirdchart, echo=FALSE, warning=FALSE}
source("scripts/thirdchart.R")
plot_hiv_per_region(hiv_df)
```

```{r secondchart.R, echo=FALSE}
source("scripts/secondchart.R")
Art_treated_vs_sick(hiv_df)
```
